R Notebook

### 2022-02-15 docs/3. SNA - Assignments/sna_Week3/Week3_Notebook.Rmd
2.15.22
opswdefopajwfgjQ"pfnetwork_statnetEA

```{r}
vectordata=as.vector(mtrxIt)
print(smugCov_ntWrk)
```

@@

setwd("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA - Assignments")

@@

# Network: Creating network Data
```{r HOLD: EDGELIST: IGRAPH: create a network object from the dataset, eval=FALSE, include=FALSE}
colnames(smugCovIdx )

@@

V(sourceEL_ig)$dnkName<-
  temp$dnkIng[
    match(V
          (sourceEL_ig)$name,
          temp$dnkIng)
  ]
print(sourceEL_ig )
edge_attr(sourceEL_ig)

#########
########
          smugEL_sn  <- sourceEL_sn
          smugEL_ig <- sourceEL_ig
dim(smug_sn)
```

# Network Info
## Basic R: Brief Dataset Description
```{r Network: Identify critical features, echo=FALSE}

#**Statnet EdgeList**   smugEL_sn
#####
#### class of an object
class(smugEL_sn )
class(smugEL_ig )

# list the structure of smugCovIdx
str(smugEL_sn )
str(smugEL_ig )

View(smug_sn)
View(smug_ig)
```

## Directed Adjacency Matrix: Create & Describe

iGraph and Statnet both use {r graph4} for
Directed Adjacency Matrix Objects

```{r graph4, statnet: Directed: Adjacency Network, echo=TRUE}

    smugCovIdx.stat<-
        network(
        smugCovIdx,
        directed=F,
        matrix.type="adjacency"
        )

#     provides a description of several critical network features
    print(source.stat)

@@

```{r graph4, igraph: Directed: Adjacency Network, echo=TRUE}

    source.ig<-
      graph.adjacency(
      flo,
      mode="undirected"
      ) 
    print(source.ig)
```

@@

#     Count Vertices
    vcount(source.ig)

#     Count Edges
    ecount(source.ig)

# Is this a Bipartite or single mode network?
    is_bipartite(source.ig)

#  Are edges directed or undirected?
    is_directed(source.ig)

#Are edges weighted or unweighted?
    is_weighted(source.ig)

@@

#     access vertex attributes
  head(source.stat %v% "vertex.names")

#      list the names of vertex attributes
  network::list.vertex.attributes(source.stat)

#     access edge attribute
  head(source.stat%e% "weight")

#  Generate a list the names of edge attributes
  network::list.edge.attributes(source.stat)

#   summarize numeric network attribute
  summary(source.stat  %v% "name")

@@

#     access vertex attribute 
  V(source.ig)$name
#     Generate a list the names of vertex attributes
  igraph::vertex_attr_names(source.ig)

#     access edge attribute
  E(source.ig)$weight

#   Generate a list the names of edge attributes  
  igraph::edge_attr_names(source.ig)

#   summarize numeric network attribute
  summary(E(source.ig)$weight)

@@

##    *Identify format of data set (i.e., matrix or
    edgelist, directed or not, weighted or not),
    and*

@@

```{r Network Attributes, echo=TRUE}

  network(smugCovIdx)

@@

#     Calculate distances between two nodes
    distances(source.ig,"node 1","node 2")

#     Calculate distance between two nodes using unweighted edges
    distances(source.ig,"node 1", "node 5",weights=NA)

@@

#     isolating the distances between specific node
    all_shortest_paths(source.ig,"node 3","node 4", weights=NA)$res
## Note: manually tell igraph to ignore edge weights.
```

@@

#     find average shortest path for network
    average.path.length(source.ig,directed=F)

@@

    sna::dyad.census(source.stat)

@@

  igraph::dyad.census(source.ig)

@@

Classifies all triads in the network. The triad
census provides a fundamental descriptive insight
into the types of triads found in a particular
dataset.

@@

#     Classify all Triad in the network: Directed Network
  sna::triad.census(source.stat, mode= )

#     Classify all Triad in the network: Undirected Network
   sna::triad.census(source.stat, mode="graph")

#     total number of all four triad types returned by triad census
   sum(sna::triad.census(source.stat, mode="graph"))

@@

```{r iGraph: Triad Census, echo=TRUE}
#Classify all Triad in the network
     igraph::triad_census(source.ig)

@@

#     network transitivity:
    transitivity(source.ig)

#     weighted network transitivity:
#   igraph::transivity(source.ig)

@@

#     Directed Networks transitivity:
  gtrans(source.stat)

@@

#     Retrive a list of the vertices we are interested
    V(source.ig)[c("node 1" ,
                "node 5", 
                "node 6",
                "node 2")]

#     check ego network transitivity
transitivity(source.ig,
             type="local", 
             vids=V(source.ig)
             [c("node 1",
                "node 5", 
                "node 6",
                "node 2")]) 
#     get global clustering cofficient
  transitivity(source.ig, type="global")

#     get average local clustering coefficient
  transitivity(source.ig, type="average")

>>>>

@@

setwd("C:/Users/white/iCloudDrive/Documents/1_DACSS_UMassAmherst/Dacss_RProjects/3. Sp22_rProjects/Dacss_679- Coursework/GIT-ajw_Learning-SocialNetworkAnalysis/docs/3. SNA - Assignments/sna_Week3")

@@

# Network: Creating network Data
```{r HOLD: EDGELIST: IGRAPH: create a network object from the dataset, eval=FALSE, include=FALSE}

colnames(smugCovIdx )

@@

V(sourceEL_ig)$dnkName<-
  temp$dnkIng[
    match(V
          (sourceEL_ig)$name,
          temp$dnkIng)
  ]
# print(sourceEL_ig )
# edge_attr(sourceEL_ig)

#########
########
          smugEL_sn  <- sourceEL_sn
          smugEL_ig <- sourceEL_ig

@@

# Network Info
  Network Objects: EDGE LIST
                  STATNET: smugEL_sn
                  IGRAPH: smugEL_ig

## Smuggler's Cove Index- NETWORK: EDGELIST: Features & Descriptions
```{r Network: Identify critical features, echo=FALSE}

#**Statnet EdgeList**   smugEL_sn
#####

```{r STATNET: Network Description}

      # class of an object
class(smugEL_sn )

      # list the structure of smugCovIdx
str(smugEL_sn )

      ## Network Attributes
 print(smugEL_sn)
          # Vertices =  
          # Directed = 
          # hyper = 
          # loops = 
          # multiple = 
          # bipartite = 
          # total edges = 
                # missing edges =
                # non-missing edges = 
          # Vertex attribute names:
          # Edge Attribute Names: 
```

@@

      # class of an object
    class(smugEL_ig )

        # list the structure of smugCovIdx
    str(smugEL_ig )

## Network Size
      # Count Vertices
    vcount(smugEL_ig)

      # Count Edges
    ecount(smugEL_ig)

## Network Mode
    # Bipartitie / Unimodal
    is_bipartite(smugEL_ig)

## Edges    
    # Un/directed 
    is_directed(smugEL_ig)

    # weighted or unweighted?
    is_weighted(smugEL_ig)

@@

# class of an object
    class(smugEL_sn)

#     access vertex attributes
  head(smugEL_sn %v% "vertex.names")

#      list the names of vertex attributes
  network::list.vertex.attributes(smugEL_sn)

#     access edge attribute
#  head(smugEL_sn%e% "weight")

#  Generate a list the names of edge attributes
  network::list.edge.attributes(smugEL_sn)

#   summarize numeric network attribute
  summary(smugEL_sn  %v% "name")

@@

#     access vertex attribute 
  V(smugEL_ig)$name
#     Generate a list the names of vertex attributes
  igraph::vertex_attr_names(smugEL_ig)

#     access edge attribute
  E(smugEL_ig)$weight

#   Generate a list the names of edge attributes  
  igraph::edge_attr_names(smugEL_ig)

@@

@@

@@

#     Calculate distances between two nodes
    distances(smugEL_ig,"node 1","node 2")

#     Calculate distance between two nodes using unweighted edges
    distances(smugEL_ig,"node 1", "node 5",weights=NA)

@@

#     isolating the distances between specific node
    all_shortest_paths(smugEL_ig,"node 3","node 4", weights=NA)$res
## Note: manually tell igraph to ignore edge weights.
```

@@

#     find average shortest path for network
    average.path.length(smugEL_ig,directed=F)

@@

    sna::dyad.census(smugEL_sn)

@@

  igraph::dyad.census(smugEL_ig)

@@

Classifies all triads in the network. The triad
census provides a fundamental descriptive insight
into the types of triads found in a particular
smugEL_

@@

#     Classify all Triad in the network: Directed Network

  sna::triad.census(smugEL_sn, mode= )

#     Classify all Triad in the network: Undirected Network
   sna::triad.census(smugEL_sn, mode="graph")

#     total number of all four triad types returned by triad census
   sum(sna::triad.census(smugEL_sn, mode="graph"))

@@

```{r iGraph: Triad Census, echo=TRUE}
#Classify all Triad in the network
     igraph::triad_census(smugEL_ig)

@@

#     network transitivity:
    transitivity(smugEL_ig)

#     weighted network transitivity:
#   igraph::transivity(smugEL_ig)

@@

#     Directed Networks transitivity:
  gtrans(smugEL_sn)

@@

#     Retrive a list of the vertices we are interested
    V(smugEL_ig)[c("node 1" ,
                "node 5", 
                "node 6",
                "node 2")]

#     check ego network transitivity
transitivity(smugEL_ig,
             type="local", 
             vids=V(smugEL_ig)
             [c("node 1",
                "node 5", 
                "node 6",
                "node 2")]) 
#     get global clustering cofficient
  transitivity(smugEL_ig, type="global")

#     get average local clustering coefficient
  transitivity(smugEL_ig, type="average")
